Efficient Coalition Formation for Web Services

### 2013-03-08 papers/coalition/coalition.tex
Changes

\begin{equation*}
v(C) = \sum_{m=metrics}{ \Big( \sum_{ws \in C}{QoS^m_{ws} \times CC^{m} \times MS_{ws} \Big) } \times w_{m} }
\end{equation*}

$CC^{m}$ is \emph{Collabrative Coefficient} for each QoS metric (non-functional parameter), it determines how web services providing that QoS metric individually will be effected in a coalition environment. If it is more than 1, is means they increase performance by working together and they are \emph{super additive}, otherwise it depicts they would perform better in linear sense if they worked alone. $w_m$ is the weight of important for a QoS metric, it gives the community the flexibility to emphasize or neglect a specific QoS parameter. Note that $ \sum_{m}{w_m} = 1 $. In this scenario we have no master web services, we assume they either dynamically vote for one, or collaborate and agree on decisions and distribute task in round robin or fair fashion. We use the same merge-and-split algorithm like ``Web Services and Many Communities'' scenario, to find stable coalitions of web serivces.

>>>>

\begin{equation}
v(C) = \sum_{m=metrics}{ \Big( \sum_{ws \in C}{QoS^m_{ws} \times MS_{ws} \Big) } \times w_{m} }
\end{equation}

%$CC^{m}$ is \emph{Collabrative Coefficient} for each QoS metric (non-functional parameter), it determines how web services providing that QoS metric individually will be effected in a coalition environment. If it is more than 1, is means they increase performance by working together and they are \emph{super additive}, otherwise it depicts they would perform better in linear sense if they worked alone. 
$w_m$ is the weight of important for a QoS metric, it gives the community the flexibility to emphasize or neglect a specific QoS parameter. Note that $ \sum_{m}{w_m} = 1 $. In this scenario we have no master web services, we assume they either dynamically vote for one, or collaborate and agree on decisions and distribute task in round robin or fair fashion. We use the same merge-and-split algorithm like ``Web Services and Many Communities'' scenario, to find stable coalitions of web serivces.
